Draft_Application_Stochastic_Volatility

### 2021-08-10 Real Dataset SV.Rmd
Aggiunta parte SV aggiornata

When focusing the attention on specific filters, first we can discuss the effect of resampling. Indeed, in the plot referring to the Sequential Importance Sampling procedure, the sequence of filtered volatilities is not able to reproduce the peaks as in with other filters, but also is characterized by collapsing confidence intervals. This is because ::::::: \
Then, if we instead look at the filtered volatilities obtained with resampling, we can appreciate how the filtered sequences for the Basic,\footnote{By this name, we refer to a particle filter that features no adaptive resampling; rather, resampling is conducted at each step of the algorithm.} Bootstrap, Auxiliary and Optimal Kernel Guided particle filters give rather analogous results, with no differences appearing at a first visual inspection.\footnote{Except for the Auxiliary Particle filtered sequence of volatilities, showing a slightly higher peak corresponding to the greatest volatility fluctuation in 2020, if compared to other filters in this subset. This is still valid for all three indices.} \
However, the sequence of filtered volatilities obtained by applying the Liu and West filter is clearly different from the others. Indeed, it shows a "more detailed" sequence of states (in the sense of the sequence of filtered volatilities being less smooth) and also a higher peak for the wide fluctuation corresponding to the 2020 Covid Crisis outbreak. Therefore, we may expect that, compared to other filtering techniques, it can provide a better representation of the data. This is because ... \textit{Potremmo parlare di maggiore sensibilità alle oscillazioni dei prezzi, o simili}

>>>>

When focusing the attention on specific filters, first we can discuss the effect of resampling. Indeed, in the plot referring to the Sequential Importance Sampling procedure, the sequence of filtered volatilities is not able to reproduce the peaks detected by all the other filters, often pointing at completely different timing and extents of such peaks. Then, if we instead look at the filtered volatilities obtained with resampling, we can appreciate how the filtered sequences for the Basic,\footnote{By this name, we refer to a particle filter that features no adaptive resampling; rather, resampling is conducted at each step of the algorithm.} Bootstrap, Auxiliary and Optimal Kernel Guided particle filters give rather analogous results, with no differences appearing at a first visual inspection.\
However, the sequence of filtered volatilities obtained by applying the Liu and West filter is somewhat different from the others. Indeed, it shows a "more detailed" sequence of states, meaning that the sequence of filtered volatilities is less smooth and features wider oscillations, with seemingly higher responsiveness to sudden changes in the observations. Therefore, we may expect that, compared to other filtering techniques, it can provide a better representation of the data.
